Tools and Ideas for the Proceedural Generation of Shadow Sculptures.

### 2015-12-15 paper/paper.tex
Working on formatting
Fix up the pseudcode a bit.

\begin{alltt}
for each sphere in spheres:
  if the sphere is entirely above the light or below the shadow plane:
    it casts no shadow; continue to the next sphere
  if the top of the sphere is beneath the light and the bottom is above the plane:
    The shadow cast on the plane will be elliptical.
    Calculate the equation of the cone formed by all lines passing through the
        light source and tangent to the sphere.
    Find the equation of the ellipse by intersecting this cone with the shadow
        plane.
    The equation has the form A*x^2 + B*y^2 + C*x*y + D*x + E*y + F = 0.
    Rearrange the equation to have the form G(x)*y^2 + H(x)*y + I(x) = 0, where
        G, H, and I are 2nd order or lower polynomials in x.
    For each column c in pixels:
      Find the value of x that corresponds to c.
      Calculate G(x), H(x), and I(x).
      Use the quadratic formula to find two values of y satisfying the
          equation for the boundary of the ellipse.
      Convert the values of y to row coordinates in the image.
      In column c and all rows r between the two calculated:
        color pixels[r][c] black
  if the sphere intersects the shadow plane:
    Handling this case is at least as complicated as handling a sphere strictly
        above the plane.
    The circular intersection of the circle and the plane is shadowed.
    Any additional shadowing is a subset of the elliptical shadow described in
        the previous case.
    This case is not handled by our code.
  if the sphere intersects the light:
    Color all of pixels black.
    Return from the proceedure early.
    This case is not handled by our code.
  if the top of the sphere is above the light, its bottom below the light, without
      intersecting it:
    The shadow cast is hyperbolic.
    This case is not handled by our code, but it would likely be similar to
        the case of elliptical shadows.

>>>>

\begin{alltt}
input: \(\vec{l}\) = position of light
       \(r\) = the radius of each sphere and cylinder
       \(spheres\) = a list of positions of centers of spheres
       \(cylinders\) = a list of pairs of positions specifying the end
              faces of the cylinders
output: \(pixels\) = array of black and white pixels indicating on
              which areas of the wall light is incident

initialize \(pixels\) to be uniformly white (illuminated)

for each \(sphere\) in \(spheres\):
  if the sphere is entirely above the light or below the shadow
        plane:
    it casts no shadow; continue to the next sphere
  if the top of the sphere is beneath the light and the bottom is above the plane:
    The shadow cast on the plane will be elliptical.
    Calculate the equation of the cone formed by all lines passing through the
        light source and tangent to the sphere.
    Find the equation of the ellipse by intersecting this cone with the shadow
        plane.
    The equation has the form \(A*x^2 + B*y^2 + C*x*y + D*x + E*y + F = 0\).
    Rearrange the equation to have the form \(G(x)*y^2 + H(x)*y + I(x) = 0\), where
        \(G\), \(H\), and \(I\) are 2nd order or lower polynomials in x.
    For each column c in pixels:
      Find the value of x that corresponds to c.
      Calculate G(x), H(x), and I(x).
      Use the quadratic formula to find two values of y satisfying the
          equation for the boundary of the ellipse.
      Convert the values of y to row coordinates in the image.
      In column c and all rows r between the two calculated:
        color pixels[r][c] black
  if the sphere intersects the shadow plane:
    Handling this case is at least as complicated as handling a sphere strictly
        above the plane.
    The circular intersection of the circle and the plane is shadowed.
    Any additional shadowing is a subset of the elliptical shadow described in
        the previous case.
    This case is not handled by our code.
  if the sphere intersects the light:
    Color all of pixels black.
    Return from the proceedure early.
    This case is not handled by our code.
  if the top of the sphere is above the light, its bottom below the light, without
      intersecting it:
    The shadow cast is hyperbolic.
    This case is not handled by our code, but it would likely be similar to
        the case of elliptical shadows.
